Empirical Analysis of the Role of Energy in Economic Growth

### 2013-01-28 EconGrowth.Rnw
Now creating the Cobb-Douglas parameters table exactly the way I want it.

<<Country Factors Graph>>=
createCountryFactorsGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(1, 1, 1, 1, 1) #line widths
  colors <- c("black", "black", "black", "black", "black") #line and point colors
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year, data=dataTable,
                  type=graphType,
                  par.settings = list(superpose.line = lineSpec),
                  key=list(text=list(c("k", "l", "q", "x", "u")),
                           type=graphType,
                           lines=lineSpec,
                           columns=1, x=0.0, y=0.98),
                  scales=list(cex=1.0, #controls text size on scales
                              tck=-0.5), #controls tick mark length
                  ylab="Indexed (1980=1)")
  return(graph)
}

createGDPComparisonGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  lineTypes <- c(1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(1) #line widths
  colors <- c("black") #line and point colors
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iGDP ~ Year, data=dataTable,
                  key=list(text=list(c("GDP")),
                           type=graphType,
                           lines=lineSpec,
                           columns=1, x=0.0, y=0.98),
                  type=graphType,
                  par.settings = list(superpose.line = lineSpec),
                  scales=list(cex=1.0, #controls text size on scales
                              tck=-0.5), #controls tick mark length
                  ylab="Indexed (1980=1)")
  return(graph)
}

# createGDPComparisonGraph <- function(countryName){
#   dataTable <- loadData(countryName)
#   graphType <- "l"
#   colors <- c("black", "black", "black", "black") #line and point colors
#   lineWidths <- c(1, 1, 1, 1) #line widths
#   lineTypes <- c(1, 5, 2, 4) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
#   lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
#   pointSpec <- list(col=colors)
#   graph <- xyplot(iGDP ~ iYear, data=dataTable,
#                   key=list(text=list(c("GDP")),
#                            type=graphType,
#                            lines=lineSpec,
#                            columns=1, x=0.0, y=0.98),
#                   type=graphType,
#                   par.settings = list(superpose.line = lineSpec),
# #                                      superpose.symbol = pointSpec),
#                   scales=list(cex=1.0, #controls text size on scales
#                               tck=-0.5), #controls tick mark length
#                   ylab="Indexed (1980=1)")
#   return(graph)
# 
#                     
# }

#createGDPComparisonGraph("US")

#createCountryFactorsGraph("US")
#lapply(countries, createCountryFactorsGraph)

@

@@

<<cobb-douglas>>=

@@

############
# Creates a row for the Cobb Douglas parameters table
##
cobbDouglasCountryRow <- function(countryName){
  dataCD <- cobbDouglasData(countryName)
  # Create CI ranges
  out <- cbind(countryName, 
               dataCD["- 95% CI", "lambda"], dataCD["CD", "lambda"], dataCD["+ 95% CI", "lambda"],
               dataCD["- 95% CI", "alpha"],  dataCD["CD", "alpha"],  dataCD["+ 95% CI", "alpha"],
               dataCD["- 95% CI", "beta"],   dataCD["CD", "beta"],   dataCD["+ 95% CI", "beta"])

  return(out)
}

cobbDouglasParamsTable <- function(){
  dataCD <- rbind(cobbDouglasCountryRow("US"),
                cobbDouglasCountryRow("UK"),
                cobbDouglasCountryRow("JP"),
                cobbDouglasCountryRow("CN"),
                cobbDouglasCountryRow("ZA"),
                cobbDouglasCountryRow("SA"),
                cobbDouglasCountryRow("IR"),
                cobbDouglasCountryRow("TZ"),
                cobbDouglasCountryRow("ZM"))
  colnames(dataCD) <- c("", "-95% CI", "$\\lambda$", "+95% CI", 
                        "-95% CI", "$\\alpha$",  "+95% CI",
                        "-95% CI", "$\\beta$",   "+95% CI")
  rownames(dataCD) <- countries
  print("************** Trying to print dataCD **********************")
#   print(class(dataCD))
#   print(dataCD)
  tableCD <- xtable(dataCD, caption="Cobb-Douglas, 1980-2011 or 1991-2011", digit = c(1,1, 4,4,4, 4,4,4, 4,4,4))
  #print(tableCD)
  return(tableCD)
}
cobbDouglasParamsTable()

@@

<<CD Analysis>>=
tablesCD <- lapply(countries, cobbDouglasCountryTable)
@

<<CD Results, results='asis', echo=FALSE>>=
print(cobbDouglasParamsTable(), caption.placement="top")

print(tablesCD[["US"]], caption.placement="top")
print(tablesCD[["UK"]], caption.placement="top")
print(tablesCD[["JP"]], caption.placement="top")
print(tablesCD[["CN"]], caption.placement="top")
print(tablesCD[["ZA"]], caption.placement="top")
print(tablesCD[["SA"]], caption.placement="top")
print(tablesCD[["IR"]], caption.placement="top")
print(tablesCD[["TZ"]], caption.placement="top")
print(tablesCD[["ZM"]], caption.placement="top")

# According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
# be able to use the "sanitize.text.function" parameter to allow markup in column headers. But this next
# line is not working at the present time. --MKH, 18 Jan 2012.
# print(tableCD, caption.placement="top", sanitize.text.function = function(x){x})
@

>>>>

<<Country Factors Graph, echo=FALSE>>=
createCountryFactorsGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(1, 1, 1, 1, 1) #line widths
  colors <- c("black", "black", "black", "black", "black") #line and point colors
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year, data=dataTable,
                  type=graphType,
                  par.settings = list(superpose.line = lineSpec),
                  key=list(text=list(c("k", "l", "q", "x", "u")),
                           type=graphType,
                           lines=lineSpec,
                           columns=1, x=0.0, y=0.98),
                  scales=list(cex=1.0, #controls text size on scales
                              tck=-0.5), #controls tick mark length
                  ylab="Indexed (1980=1)")
  return(graph)
}
@

@@

<<cobb-douglas, echo=FALSE>>=

@@

############
# Creates a row for the Cobb Douglas parameters table
##
cobbDouglasCountryRow <- function(countryName){
  dataCD <- cobbDouglasData(countryName)
  # Create CI ranges
  out <- cbind(dataCD["- 95% CI", "lambda"], dataCD["CD", "lambda"], dataCD["+ 95% CI", "lambda"],
               dataCD["- 95% CI", "alpha"],  dataCD["CD", "alpha"],  dataCD["+ 95% CI", "alpha"],
               dataCD["- 95% CI", "beta"],   dataCD["CD", "beta"],   dataCD["+ 95% CI", "beta"])
  return(out)
}

cobbDouglasParamsTable <- function(){
  dataCD <- rbind(cobbDouglasCountryRow("US"),
                cobbDouglasCountryRow("UK"),
                cobbDouglasCountryRow("JP"),
                cobbDouglasCountryRow("CN"),
                cobbDouglasCountryRow("ZA"),
                cobbDouglasCountryRow("SA"),
                cobbDouglasCountryRow("IR"),
                cobbDouglasCountryRow("TZ"),
                cobbDouglasCountryRow("ZM"))
  colnames(dataCD) <- c(" ", "$\\lambda$", " ", 
                        " ", "$\\alpha$",  " ",
                        " ", "$\\beta$",   " ")
  rownames(dataCD) <- countries
  tableCD <- xtable(dataCD, 
                    caption="Cobb-Douglas parameters for 1980-2011 (developed nations) or 1991-2011 (others). (Parameter estimates beneath symbol. 95\\% confidence bounds to left and right.)", 
                    digit = c(1, 4,4,4, 2,2,2, 2,2,2),
                    align = "r|ccc|ccc|ccc")
  return(tableCD)
}

@@

<<CD Results, results='asis', echo=FALSE>>=
print(cobbDouglasParamsTable(), caption.placement="top", sanitize.colnames.function = identity)
@
